% Updated Resume
\documentclass[11pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{array}
\usepackage{parskip}
\usepackage{xcolor}

\geometry{margin=0.75in}
\hypersetup{colorlinks=true, urlcolor=blue}
\setlist[itemize]{noitemsep, leftmargin=*, topsep=2pt}

% Custom colors
\definecolor{darkblue}{RGB}{0,35,102}

% Header
\begin{document}
\begin{center}
    {\LARGE \textbf{Umar Akram}} \\[2pt]
    {\normalsize Software Engineer \& AI Trainer} \\[4pt]
    \textbf{Phone:} +20 1023651704 \quad
    \textbf{Email:} \href{mailto:uamirad00@gmail.com}{uamirad00@gmail.com} \\[4pt]
    \textbf{LinkedIn:} \href{https://linkedin.com/in/umarrakram}{linkedin.com/in/umarrakram} \quad
    \textbf{GitHub:} \href{https://github.com/umarrakram}{github.com/umarrakram} \\[8pt]
\end{center}

% Professional Summary
\section*{\color{darkblue}Professional Summary}
Results-driven Software Engineer and AI Trainer with expertise in developing SwiftUI-based mobile applications and designing AI-driven educational content. Skilled in Python, C++, mathematics curriculum development, and Arabic language localization. Proven ability to enhance learner engagement and streamline training workflows, combined with a strong background in performance optimization and agile methodologies.

% Education
\section*{\color{darkblue}Education}
\textbf{Egypt-Japan University of Science and Technology} \hfill \textit{Expected June 2026} \\
Bachelor of Science in Computer Science and Information Technology \\
Alexandria, Egypt \\
\textit{Relevant Coursework:} Mobile App Development, Data Structures \& Algorithms, Software Engineering, Machine Learning

% Technical Skills
\section*{\color{darkblue}Technical Skills}
\begin{multicols}{2}
\begin{itemize}
    \item \textbf{Languages \& Frameworks:} Swift, SwiftUI, Combine, UIKit, Python, C++, Arabic
    \item \textbf{Machine Learning:} Dataset Annotation, Supervised Learning, Model Evaluation
    \item \textbf{AI Training Tools:} Label Studio, Prodigy, Jupyter Notebooks
    \item \textbf{Development Tools:} Xcode, Firebase, Git, Postman
    \item \textbf{Design Patterns:} MVVM, MVC, Clean Architecture
    \item \textbf{Concurrency:} Grand Central Dispatch (GCD), OperationQueue
    \item \textbf{Other Skills:} Agile Methodologies, CI/CD, App Store Deployment, Localization
    \item \textbf{Languages:} Arabic (Native), English (Fluent)
\end{itemize}
\end{multicols}

% Professional Experience
\section*{\color{darkblue}Professional Experience}
\textbf{Outlier} \hfill \textit{Remote / Cairo, Egypt} \\
\textit{AI Trainer} \hfill \textit{June 2023 -- February 2024}
\begin{itemize}
    \item Developed and delivered AI training modules for Outlier's platform, covering mathematics, Python, C++, and Arabic language processing.
    \item Collaborated with data scientists to refine annotation guidelines, improving dataset quality and reducing labeling errors by 25\%.
    \item Created comprehensive lesson plans and hands-on coding exercises, resulting in a 30\% increase in learner engagement and completion rates.
    \item Conducted one-on-one tutoring sessions and peer review workshops to deepen students’ understanding of complex algorithmic concepts.
    \item Localized technical content in Arabic, ensuring material accessibility and comprehension for MENA region learners.
    \item Monitored and evaluated student progress using performance metrics, adapting curriculum to address knowledge gaps and optimize learning outcomes.
\end{itemize}
\newpage
\textbf{Onvo} \hfill \textit{Cairo, Egypt} \\
\textit{iOS Developer} \hfill \textit{March 2024 -- Present}
\begin{itemize}
    \item Engineered a \textbf{SwiftUI}-based social application with real-time notifications, boosting daily active users by 40\%.
    \item Integrated \textbf{WebKit} for video streaming, implementing adaptive bitrate optimization to reduce latency by 35\%.
    \item Refactored RESTful APIs using \textbf{Vapor}, reducing server response times by 50\% through payload caching.
    \item Designed and developed Axios, an on-device code editor with syntax highlighting and real-time execution, enhancing developer productivity by 25\%.
    \item Supported simple multitasking with a round-robin scheduler and cooperative threading.
    \item Built custom inter-process communication (IPC) using message queues and shared memory.
    \item Implemented memory segmentation and paging fundamentals for task isolation.
    \item Project aimed to provide a modular and extensible core for hobby operating system development.
    \item Implemented Apple Wallet & payments: integrated Apple Pay (PassKit) and StoreKit for one-time and subscription purchases, connected Apple Pay to Stripe for tokenized payments, handled PKPaymentAuthorization flows, receipt validation and server-side verification, improving checkout conversion and reducing payment failures.
\end{itemize}

% Key Projects
\section*{\color{darkblue}Key Projects}
\textbf{Code Editor - Axios} \hfill \textit{SwiftUI, Combine, WebKit}
\begin{itemize}
    \item Built a code editor with syntax highlighting, auto-completion, and real-time execution using WebKit.
    \item Developed a custom parser supporting 10+ programming languages with 95\% execution accuracy.
    \item Integrated GitHub API for version control and collaboration.
\end{itemize}

\textbf{WeatherSnap - Forecast App} \hfill \textit{SwiftUI, Combine, Core Location}
\begin{itemize}
    \item Integrated OpenWeatherMap API with Combine for reactive data flow.
    \item Implemented GPS-based forecasts using Core Location with 98\% accuracy.
    \item Designed animated weather transitions using Lottie for enhanced user experience.
\end{itemize}

% Achievements
\section*{\color{darkblue}Achievements}
\begin{itemize}
    \item Published two iOS applications on the App Store, achieving an average rating of 4.4/5 and over 100,000 downloads.
    \item Reduced memory leaks by 40\% using Xcode Instruments and Combine.
    \item Led Agile sprints, delivering features 15\% ahead of deadlines.
\end{itemize}

\end{document}
